Causal inference is not a statistical problem

### 2023-04-05 manuscript.qmd

---
title: "Causal inference is not a statistical problem"
author: "Lucy D'Agostino McGowan"
format: pdf
execute: 
  echo: false
  message: false
  warning: false
editor_options: 
  chunk_output_type: console
bibliography: citations.bib
---

>>>>

---
title: "Causal inference is not a statistical problem"
author: 
 - "Lucy D'Agostino McGowan"
 - "Malcolm Barrett"
format: pdf
execute: 
  echo: false
  message: false
  warning: false
editor_options: 
  chunk_output_type: console
bibliography: citations.bib
---
